Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-07-31 paper/paper.tex
Fixy fixy

>>>>

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t2-vs-clique-cilk-t4.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t4-vs-clique-cilk-t8.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t8-vs-clique-cilk-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t16-vs-clique-cilk-t32.pdf}

    \caption{Scalability and reproducibility, clique algorithm, Cilk.}
\end{figure*}
